### 2018-06-02 CS761-RandomizedAlgorithms/assignments/a1.tex
writing 5c
still going

\newpage
\section{}
\subsection{a}
\paragraph{}
\begin{align*}
M_{X^2}(t) &= E[e^{tX^2}] \\
&= \int_{-\infty}^\infty e^{tx^2}f(x)dx \\
&=\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{tx^2-\frac{1}{2}x^2}dx \\
&= \int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{\frac{-1}{2}(1-2t)x^2}dx \\
&= \frac{1}{\sqrt{1-2t}}\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{z^2}dz &\text{Taking $z=\sqrt{1-2t}x$} \\
&= \frac{1}{\sqrt{1-2t}} &\text{Using $\int_{-\infty}^\infty f(x)dx = 1$}.
\end{align*}
\subsection{b}
\paragraph{}
Using Taylor expansion we have
\begin{align*}
E[X^4] = M_{X^2}^{(2)}(0).
\end{align*}
Now observe that
$$M_{X^2}^{(2)}(t) = \frac{3}{(1-2t)^{5/2}}$$
and so
$$M_{X^2}^{(2)}(0) = 3.$$
Therefore $E[X^4] = 3$.
\subsection{c}

>>>>

\newpage
\section{}
\subsection{a}
\paragraph{}
\begin{align*}
M_{X^2}(t) &= E[e^{tX^2}] \\
&= \int_{-\infty}^\infty e^{tx^2}f(x)dx \\
&=\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{tx^2-\frac{1}{2}x^2}dx \\
&= \int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{\frac{-1}{2}(1-2t)x^2}dx \\
&= \frac{1}{\sqrt{1-2t}}\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{z^2}dz &\text{Taking $z=\sqrt{1-2t}x$} \\
&= \frac{1}{\sqrt{1-2t}} &\text{Using $\int_{-\infty}^\infty f(x)dx = 1$}.
\end{align*}
\subsection{b}
\paragraph{}
Using Taylor expansion we have
\begin{align*}
E[X^4] = M_{X^2}^{(2)}(0).
\end{align*}
Now observe that
$$M_{X^2}^{(2)}(t) = \frac{3}{(1-2t)^{5/2}}$$
and so
$$M_{X^2}^{(2)}(0) = 3.$$
Therefore $E[X^4] = 3$.
\subsection{c}
\paragraph{}
We have the following
\begin{align*}
Pr(Y > 1+\epsilon) &= Pr(\sum_{i=1}^kX_i^2 > k(1+\epsilon))\\
&=Pr(e^{t\sum_{i=1}X_i^2} > e^{tk(1+\epsilon)})\\
&\leq \frac{E[e^{t\sum_{i=1}X_i^2}]}{e^{tk(1+\epsilon)}} \\
&= \frac{\Pi_{i=1}^kE[e^{t\sum_{i=1}^kX_i^2}]}{e^{tk(1+\epsilon)}} &\text{by independence}\\
&=M_{X^2}(t)^ke^{-tk(1+\epsilon)}\\
&=\sqrt{1-2t}^{-k}e^{-tk(1+\epsilon)} \\
&= (1-2t)^{-k/2}e^{-tk(1+\epsilon)}\\
&= \frac{1}{1-2t}^{k/2}e^{-tk(1+\epsilon)}
\end{align*}
